Initial Analysis

### 2019-05-28 Initial_Analysis.Rmd
Include a step to jump already computed species

@@

```{r Routine_parallel, eval = T, echo = F}

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List[1:3], FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
    )
  )
)

@@

```{r Fun_GetTransResults, eval = T}

@@

```{r Load_Data, eval = T}

>>>>

# Step to run function for species not computed
Computed_Spp <- as.integer(gsub("\\_.*","",list.files(Results_Path)))

Exploited_Species <- Exploited_Species %>%
  filter(!TaxonKey %in% Computed_Spp)

@@

```{r Routine_parallel, eval = F, echo = F}

@@

system.time(
  Spp_Trans <- bind_rows(
    mclapply(
      Exploited_Species_List, FUN =EstTransIndex, Model = "All", Neighbors = Neighbor_List,Coord = CoorG
    )
  )
)

@@

```{r Fun_GetTransResults, eval = F}

@@

```{r Load_Data, eval = F}
